---
title: "Interactive Networks among SDG Indicators"
author: "Project 2"
date: "11/23/2021"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    theme: journal
---
<style>
body{ /* Normal */
font-size: 15px;
color: black;
}
write {  
line-height: 7em;
}
table { /* Table */
font-size: 12px;
}
h1 { /* Header 1 */
font-size: 30px;
}
h2 { /* Header 2 *
font-size: 26px;
}
h3 { /* Header 3 */
font-size: 22px;
}
code.r{ /* Code block */
font-size: 14px;
}
pre { /* Code block */
font-size: 14px
}
.main-container {
    width: 80%;
    max-width: unset;
}
</style>

```{r setup, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=TRUE, message=FALSE, warning=FALSE)
```

```{r load packages, echo=FALSE, eval=TRUE}
library(readxl)
library(magrittr)
library(dplyr)
library(ggplot2)    
library(ggthemes)
library(tidyverse)
library(jsonlite)
library(tidyr)
library(tidytext)
library(textdata)
library(tm)
library(quanteda)
library(rvest)
library(stringr)
library(SnowballC)
library(wordcloud)
library(plotrix)
library(qdapDictionaries)
library(formattable)
library(stringr)
library(DT)
library(network)
library(ggnetwork)
library(igraph)
library(RColorBrewer)
library(randomcoloR)
library(stringi)
library(igraph)
library(ggraph)
library(graphlayouts)
library(visNetwork)
```
## Network visualization using output from text model

In the network graph below, the size of each vertices (each indicator) represents the number of related indicators that are connected to it. The width of the edges linking each indicator is determined according to the similarity score between each pair of related indicators. The indicators are grouped according to the goals they belong to, which are denoted by different colors of the vertices.

Please zoom in to see the indicator labels, and click/hover to see specific indicator titles and similarity scores between pairs of indicators.You could also filter according to Indicator and Goals.

```{r import data, echo=FALSE, eval=TRUE}
edgelist <- read.csv("../../../Data/Text_Model_Data/edgelist.csv")
```

```{r, text titles, echo=FALSE, eval=TRUE}
indicator_info <- read.csv("../../../Data/Text_Model_Data/indicator_att.csv")
Textdata <- datatable(indicator_info, rownames=TRUE, caption=htmltools::tags$caption(style="caption-side: bottom; text-align: center;", "Innovative counties in the U.S."), filter="top", extensions="Buttons", options=list(dom = "Bfrtip", buttons = c("colvis", "copy", "csv", "excel", "pdf", "print")))
```

```{r create nodes, echo=FALSE, eval=TRUE}
nodes <- edgelist %>%
  select(indicator, related_indicator)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
```

```{r, Interactive Text Network, echo=FALSE, eval=TRUE}

edges <- edgelist %>% dplyr::rename(Indicator = indicator)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree*10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$similarity_score*10, color="gray",title = paste("Similarity score:",edges$similarity_score), smooth = FALSE, shadow = FALSE)

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Text Network Model",submain= "UN SDG Indicator Metadata", footer="Zoom in to see indicator name, click/hover to see indicator title/similarity score between each pair of indicators") %>%
  visOptions(selectedBy = "Goal", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Text Network Model.html")
```



## Network visualization using output from the social network model

In the network graph below, the size of each vertices (each indicator) represents the number of related indicators that are connected to it. The width of the edges linking each indicator is determined according to the similarity score between each pair of related indicators, and the color of the egdes is green if it's a positive correlation, and red if it's a negative correlation. The indicators are grouped according to the goals they belong to, which are denoted by different colors of the vertices.

Please zoom in to see the indicator labels, and click/hover to see specific indicator titles and similarity scores between pairs of indicators. You could also filter according to Indicator and Goals.

### Indonesia
```{r import Indonesia network coefficients, echo=FALSE, eval=TRUE}
edgelist <- read.csv("~/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/indo_coefficients_sig.csv")
#Some preprocessing
edgelist<-edgelist%>%
  select(Var1, Var2, value)%>%
  filter(Var1!=Var2)
```

```{r Indonesia nodes, echo=FALSE, eval=TRUE}
nodes <- edgelist %>%
  select(Var1, Var2)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g2<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g2, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
```

```{r Indonesia Network, echo=FALSE, eval=TRUE, fig.height=10, fig.width=10}
edges <- edgelist %>% dplyr::rename(Indicator = Var1, related_indicator = Var2)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree/10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$value, color=ifelse(edges$value>0, "green", "red"),title = paste("Coefficient value:",edges$value), smooth = FALSE, shadow = FALSE)

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Social Network Model-Indonesia",submain= "UN SDG Indicator Database", footer="Zoom in to see indicator name, click/hover to see indicator title/coefficients") %>%
  visPhysics(maxVelocity = 30) %>%
  visOptions(selectedBy = "Goal",
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Social Network Model-Indonesia.html")
```

### Guatemala 
```{r import Guatemala network coefficients, echo=FALSE, eval=TRUE}
edgelist <- read.csv("~/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/gua_coefficients_sig.csv")
#Some preprocessing
edgelist<-edgelist%>%
  select(Var1, Var2, value)%>%
  filter(Var1!=Var2)
```

```{r Guatemala nodes, echo=FALSE, eval=TRUE}
nodes <- edgelist %>%
  select(Var1, Var2)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g3<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g3, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
```

```{r Guatemala Network, echo=FALSE, eval=TRUE, fig.height=10, fig.width=10}

edges <- edgelist %>% dplyr::rename(Indicator = Var1, related_indicator = Var2)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree/10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$value, color=ifelse(edges$value>0, "green", "red"),title = paste("Coefficient value:",edges$value), smooth = FALSE, shadow = FALSE)

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Social Network Model-Guatemala",submain= "UN SDG Indicator Database", footer="Zoom in to see indicator name, click/hover to see indicator title/coefficients") %>%
  visPhysics(maxVelocity = 30) %>%
  visOptions(selectedBy = "Goal", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Social Network Model-Guatemala.html")
```