---
title: "R Notebook"
output: html_notebook
---

---
title: "Interactive Networks"
author: "Li Peishan"
date: "11/23/2021"
output:
  html_notebook:
    toc: yes
    theme: journal
---
<style>
body{ /* Normal */
font-size: 15px;
color: black;
}
write {  
line-height: 7em;
}
table { /* Table */
font-size: 12px;
}
h1 { /* Header 1 */
font-size: 30px;
}
h2 { /* Header 2 *
font-size: 26px;
}
h3 { /* Header 3 */
font-size: 22px;
}
code.r{ /* Code block */
font-size: 14px;
}
pre { /* Code block */
font-size: 14px
}
.main-container {
    width: 80%;
    max-width: unset;
}
</style>

```{r setup, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=TRUE, message=FALSE, warning=FALSE)
```

```{r load packages, echo=FALSE, eval=TRUE}
library(readxl)
library(magrittr)
library(dplyr)
library(ggplot2)    
library(ggthemes)
library(tidyverse)
library(jsonlite)
library(tidyr)
library(tidytext)
library(textdata)
library(tm)
library(quanteda)
library(rvest)
library(stringr)
library(SnowballC)
library(wordcloud)
library(plotrix)
library(qdapDictionaries)
library(formattable)
library(stringr)
library(DT)
library(network)
library(ggnetwork)
library(igraph)
library(RColorBrewer)
library(randomcoloR)
library(stringi)
library(igraph)
library(ggraph)
library(graphlayouts)
library(visNetwork)
```
# Network visualization using output from text model
## Data preparation
```{r import data, echo=TRUE, eval=TRUE}
edgelist <- read.csv("../../../Data/Text_Model_Data/edgelist.csv")
edgelist
```
Indicator title
```{r, text titles, echo=TRUE, eval=TRUE}
indicator_info <- read.csv("../../../Data/Text_Model_Data/indicator_att.csv")
library(stringr)
str_replace_all(indicator_info$Indicator, fixed(" "), "")
Textdata <- datatable(indicator_info, rownames=TRUE, caption=htmltools::tags$caption(style="caption-side: bottom; text-align: center;", "Innovative counties in the U.S."), filter="top", extensions="Buttons", options=list(dom = "Bfrtip", buttons = c("colvis", "copy", "csv", "excel", "pdf", "print")))
Textdata
```
For future classification of indicators into the goals they belong to, create the nodes dataframe:
```{r create nodes, echo=TRUE, eval=TRUE}
nodes <- edgelist %>%
  select(indicator, related_indicator)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
str_replace_all(nodes$Indicator, fixed(" "), "")
#nodes$goal <- stri_match_first_regex(nodes$indicator, "(.*?)\\.")[,2]
#nodes$goal <-as.numeric(nodes$goal)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
str_replace_all(in_degree$Indicator, fixed(" "), "")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
nodes
```
## Visualization
In the network graph below, the size of each vertices (each indicator) represents the number of related indicators that are connected to it. The width of the edges linking each indicator is determined according to the similarity score between each pair of related indicators. The indicators are grouped according to the goals they belong to, which are denoted by different colors of the vertices.

```{r, Interactive Text Network, echo=TRUE, eval=TRUE}

edges <- edgelist %>% dplyr::rename(Indicator = indicator)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree*10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$similarity_score*10, color="gray",title = paste("Similarity score:",edges$similarity_score), smooth = FALSE, shadow = FALSE)

nodes
edges

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Text Network Model",submain= "UN SDG Indicator Metadata", footer="Zoom in to see indicator name, click/hover to see indicator title") %>%
  visOptions(selectedBy = "Goal", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Text Network Model.html")
```
# Network visualization using output from the social network model
## Indonesia
###Data preparation
```{r import Indonesia network coefficients, echo=TRUE, eval=TRUE}
edgelist <- read.csv("~/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/indo_coefficients_sig.csv")
#Some preprocessing
edgelist<-edgelist%>%
  select(Var1, Var2, value)%>%
  filter(Var1!=Var2)
edgelist
```
For future classification of indicators into the goals they belong to, create the nodes dataframe:
```{r Indonesia nodes, echo=TRUE, eval=TRUE}
nodes <- edgelist %>%
  select(Var1, Var2)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g2<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g2, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
nodes
```
### Visualization
```{r Indonesia Network, echo=TRUE, eval=TRUE, fig.height=10, fig.width=10}
edges <- edgelist %>% dplyr::rename(Indicator = Var1, related_indicator = Var2)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree/10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$value, color=ifelse(edges$value>0, "green", "red"),title = paste("Coefficient value:",edges$value), smooth = FALSE, shadow = FALSE)

nodes
edges

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Social Network Model-Indonesia",submain= "UN SDG Indicator Database", footer="Zoom in to see indicator name, click/hover to see indicator title") %>%
  visPhysics(maxVelocity = 30) %>%
  visOptions(selectedBy = "Goal",
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Social Network Model-Indonesia.html")
```

## Guatemala 
### Data preparation
```{r import Guatemala network coefficients, echo=TRUE, eval=TRUE}
edgelist <- read.csv("~/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/gua_coefficients_sig.csv")
#Some preprocessing
edgelist<-edgelist%>%
  select(Var1, Var2, value)%>%
  filter(Var1!=Var2)
edgelist
```
For future classification of indicators into the goals they belong to, create the nodes dataframe:
```{r Guatemala nodes, echo=TRUE, eval=TRUE}
nodes <- edgelist %>%
  select(Var1, Var2)
nodes <- data.frame(Indicator = unlist(nodes, use.names = FALSE))
nodes <- distinct(nodes)
nodes<-merge(x=nodes,y=indicator_info,by="Indicator",all.x=TRUE)
g3<-graph_from_data_frame(edgelist, directed=FALSE, vertices=nodes)
in_degree<-degree(g3, mode="in")
in_degree<-as.data.frame(in_degree)
in_degree <- cbind(rownames(in_degree), in_degree)
rownames(in_degree) <- NULL
colnames(in_degree) <- c("Indicator","in_degree")
nodes<-merge(x=nodes,y=in_degree,by="Indicator",all.x=TRUE)
nodes<-nodes %>%
  arrange(Goal)
nodes<-nodes %>%
  select(Indicator, Goal, Indicator_title, in_degree)
nodes
```
### Visualization
```{r Guatemala Network, echo=TRUE, eval=TRUE, fig.height=10, fig.width=10}

edges <- edgelist %>% dplyr::rename(Indicator = Var1, related_indicator = Var2)

nodes <- data.frame(id = nodes$Indicator,
                    label = nodes$Indicator,
                    group = nodes$Goal,
                    Goal = nodes$Goal,
                    shape = "dot",
                    shadow = FALSE,
                    color = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    highlight = ifelse(nodes$Goal == 1,"#ea1d2d",ifelse(nodes$Goal == 2,"#d19f2a",ifelse(nodes$Goal == 3,"#2d9a47",
                            ifelse(nodes$Goal == 4,"#c22033",ifelse(nodes$Goal == 5,"#ef412a",ifelse(nodes$Goal == 6,"#00add8",
                            ifelse(nodes$Goal == 7,"#fdb714",ifelse(nodes$Goal == 8,"#8f1838",ifelse(nodes$Goal == 9,"#f36e24",
                            ifelse(nodes$Goal == 10,"#e01a83",ifelse(nodes$Goal == 11,"#f99d25",ifelse(nodes$Goal == 12,"#cd8b2a",
                            ifelse(nodes$Goal == 13,"#48773c",ifelse(nodes$Goal == 14,"#007dbb",ifelse(nodes$Goal == 15,"#40ae49",
                            ifelse(nodes$Goal == 16,"#00558a","#1a3668")))))))))))))))),
                    size = nodes$in_degree/10, title = paste(nodes$Indicator,nodes$Indicator_title))

edges <- data.frame(from = edges$Indicator, to=edges$related_indicator, width = edges$value, color=ifelse(edges$value>0, "green", "red"),title = paste("Coefficient value:",edges$value), smooth = FALSE, shadow = FALSE)

nodes
edges

visnet<-visNetwork(nodes,edges, height = "700px", width = "100%", main="Social Network Model-Guatemala",submain= "UN SDG Indicator Database", footer="Zoom in to see indicator name, click/hover to see indicator title") %>%
  visPhysics(maxVelocity = 30) %>%
  visOptions(selectedBy = "Goal", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visGroups(groupname = "1", shape="dot", color = "#ea1d2d") %>%
  visGroups(groupname = "2",  shape="dot",color = "#d19f2a") %>%
  visGroups(groupname = "3",  shape="dot",color = "#2d9a47") %>%
  visGroups(groupname = "4",  shape="dot",color = "#c22033") %>%
  visGroups(groupname = "5",  shape="dot",color = "#ef412a") %>%
  visGroups(groupname = "6",  shape="dot",color = "#00add9") %>%
  visGroups(groupname = "7",  shape="dot",color = "#fdb714") %>%
  visGroups(groupname = "8",  shape="dot",color = "#8f1838") %>%
  visGroups(groupname = "9",  shape="dot",color = "#f36e24") %>%
  visGroups(groupname = "10", shape="dot", color = "#e01a83") %>%
  visGroups(groupname = "11",  shape="dot",color = "#f99d25") %>%
  visGroups(groupname = "12",  shape="dot",color = "#cd8b2a") %>%
  visGroups(groupname = "13", shape="dot", color = "#48773c") %>%
  visGroups(groupname = "14",  shape="dot",color = "#007dbb") %>%
  visGroups(groupname = "15", shape="dot", color = "#40ae49") %>%
  visGroups(groupname = "16",  shape="dot",color = "#00558a") %>%
  visGroups(groupname = "17",  shape="dot",color = "#1a3668") %>%
  visLegend(main="Legend", position="right", ncol=3, width=0.2)
visnet
visSave(visnet, file = "Social Network Model-Guatemala.html")
```