---
title: "QAP regression"
author: "Qinyue Hao"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(network)
library(sna)
library(dplyr)
```


**We need to admit: caveats of statistical inference with networks:**
In networks: Non-independence of observations
The inference problem: The non-independence of observations affects the standard errors, not the coefficients. 
To relieve this problem, we adjust standard errors by permuting rows and columns in the matrix, while maintaining the underlying relationship. -- QAP
**QAP – the Quadratic Assignment Procedure** - https://www.stata.com/meeting/1nasug/simpson.pdf


# Part 1: real number matrices

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net_weighted.RData")
indo_cm <- cm

# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net_weighted.RData")
gua_cm <- cm

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```

## 1. QAP between text similarity and correlation coefficients

### Use the original value of similarity scores in text network and correlation coefficients in Indictor networks, to see:  How much the similarity between Indicator descriptions predict the correlation coefficient between their measurements?

### 1) Indonesia

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cm), rownames(indo_cm)]

# install.packages("sna")
library(sna)
# indo_nl_tc <- netlm(indo_tm, indo_cm)
# summary(indo_nl_tc)
indo_nl_ct <- netlm(indo_cm, indo_tm)
summary(indo_nl_ct)
```

Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are
correlated at sqrt(0.0005801, which is the R-squared)=0.02408527, with p=0.03508, statistically significant.



### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cm), rownames(gua_cm)]

# install.packages("sna")
library(sna)
# gua_nl_tc <- netlm(gua_tm, gua_cm)
# summary(gua_nl_tc)
gua_nl_ct <- netlm(gua_cm, gua_tm)
summary(gua_nl_ct)
```

Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are
correlated at sqrt(0.007584, which is the R-squared)=0.08708616, with p=1.163e-12, statistically significant.


## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Indonesia predict that of Guatemala?

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)
# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)
```

Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are
correlated at sqrt(0.0001961, which is the R-squared)=0.01400357, with p=0.2779, not statistically significant.
	

# Part 2: binary matrices

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net_weighted.RData")
indo_cm <- cm

# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net_weighted.RData")
gua_cm <- cm

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```


```{r}
indo_cm[indo_cm >= -0.5 & indo_cm < 0.5] <- 0
indo_cm[indo_cm <= -0.5 | indo_cm >= 0.5] <- 1

gua_cm[gua_cm >= -0.5 & gua_cm < 0.5] <- 0
gua_cm[gua_cm <= -0.5 | gua_cm >= 0.5] <- 1

tm[tm < 0.2] <- 0
tm[tm >= 0.2] <- 1
```


### 1) Indonesia

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cm), rownames(indo_cm)]

# install.packages("sna")
library(sna)
indo_nl_ct <- netlm(indo_cm, indo_tm)
summary(indo_nl_ct)

# indo_nl_tc <- netlm(indo_tm, indo_cm)
# summary(indo_nl_tc)
```

Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Indicator text network (whether indicator description similarity >= 0.2) with OLS network model shows that they are
correlated at sqrt(0.0005522, which is the R-squared)=0.02349894, with p=0.03978, statistically significant.


```{r}
indo_nlo_ct <- netlogit(indo_cm, indo_tm)
summary(indo_nlo_ct)
```
Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Indicator text network (whether indicator description similarity >= 0.2) with Network Logit Model shows that with the Indicator text network, we can predict the Indonesia coefficient network with an 67.3% accuracy.


Contingency Table (predicted (rows) x actual (cols)):    
       0      1         
0      0      0           
1   2504   5152             

	**Total Fraction Correct: 0.6729363**          
	Fraction Predicted 1s Correct: 0.6729363          
	Fraction Predicted 0s Correct: NaN          
	False Negative Rate: 0           
	False Positive Rate: 1             




### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cm), rownames(gua_cm)]

# install.packages("sna")
library(sna)
gua_nl_tc <- netlm(gua_tm, gua_cm)
summary(gua_nl_tc)

gua_nl_ct <- netlm(gua_tm, gua_cm)
summary(gua_nl_ct)
```


Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Indicator text network (whether indicator description similarity >= 0.2) with OLS network model shows that they are
correlated at sqrt(0.0005318, which is the R-squared)=0.02306079, with p=0.0602, statistically significant(p < 0.1).


```{r}
gua_nlo_ct <- netlogit(gua_cm, gua_tm)
summary(gua_nlo_ct)
```

Predicting the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala text network (whether indicator description similarity >= 0.2) with Network Logit Model shows that with the Guatemala text network, we can predict the Indonesia coefficient network with an 75.3% accuracy.


Contingency Table (predicted (rows) x actual (cols)):    
       0      1
0      0      0
1   1636   5006

	**Total Fraction Correct: 0.7536886** 
	Fraction Predicted 1s Correct: 0.7536886 
	Fraction Predicted 0s Correct: NaN 
	False Negative Rate: 0 
	False Positive Rate: 1             
 
 
 
## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Indonesia predict that of Guatemala?

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)

# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)
```
> Predciting the Indonesia indicator network from the Guatemala indicator network shows that they are correlated at sqrt(0.07866, which is the R-squared)=0.0.8869047, with p=0, statistically significant.


```{r}
nlo_2country <- netlogit(indo_cm2, gua_cm2)
summary(nlo_2country)
```

Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) with Network Logit Model shows that with the Guatemala text network, we can predict the Indonesia coefficient network with an 68.4% accuracy.


Contingency Table (predicted (rows) x actual (cols)):           
         Actual
Predicted      0      1
        0    922    638
        1   1260   3186

	**Total Fraction Correct: 0.6839827** 
	Fraction Predicted 1s Correct: 0.7165992 
	Fraction Predicted 0s Correct: 0.5910256 
	False Negative Rate: 0.166841 
	False Positive Rate: 0.5774519            
           
	


```{r}
tm2 <- tm[colnames(gua_cm2), colnames(gua_cm2)] # colnames(indo_cm2) and colnames(gua_cm2) are the same
cm_tm <- array(NA, c(2, length(gua_cm2[1,]),length(gua_cm2[1,]))) 
cm_tm[1,,] <- gua_cm2
cm_tm[2,,] <- tm2
n2<-netlm(indo_cm2, cm_tm)
summary(n2)

```
Predicting the Indonesia indicator coefficient network from the Guatemala indicator coefficient network and the Text network shows, **net of each other**, the Guatemala indicator coefficient network network is more than 3x (0.307 [p=0.001] vs. 0.081 [p=0.313]) better as a predictor of Indonesia indicator correlations.

This multiple network OLS regression here is **not a good practice**, because the Indonesia and Guatemala coefficient networks are two different data objects, we can not and should not hold one constant to see the relationship between the other and the text network. 

However, it suggests a way to go in further studies -- multiple network regressions, which may be helpful when we have more than two various types networks for the same country, for example, on the target level, 1) target coefficient network, 2)target description text network, 3)target progress network (suggesting whether the target was achieved on time).

