---
title: "ERGMs"
author: "Qinyue Hao"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(network)
library(sna)
library(dplyr)
# install.packages("RCurl")
# install.packages("ergm")
library(RCurl)
library(ergm)
```


# ERGMs -- Exponential Random Graph Models                
## Another way to model relations             
- Remember the problem:             
  - We have deep dependence in our data (clustering)            
- We have structural properties about our network that might matter 


## How ERGMs work
- From Cranmer & Desmarais (p.71): The only assumptions we have to
make about ERGMs are (1) that we observe the expected values of a
bunch of parameters that define a network, Γi, and (2) that we have
identified the factors that influence the probability of observing any
given graph (i.e., the model is correctly specified). ERGMs thus
provide a method capable of estimating standard covariate effects as
well as the effects of other network properties without having to make
any assumptions about independence.



First, read in the matrices:

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/indo_coefficient_matrix.RData")
indo_cm <- x
# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/gua_coefficient_matrix.RData")
gua_cm <- x

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```

```{r}
indo_cm[indo_cm >= -0.5 & indo_cm < 0.5] <- 0
indo_cm[indo_cm <= -0.5 | indo_cm >= 0.5] <- 1

gua_cm[gua_cm >= -0.5 & gua_cm < 0.5] <- 0
gua_cm[gua_cm <= -0.5 | gua_cm >= 0.5] <- 1

tm[tm < 0.2] <- 0
tm[tm >= 0.2] <- 1
```


Second, read in their attribute tables:

```{r}
# use the catt (coefficient network attribute form) from the network we built before
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net.RData")
indo_catt <- catt
# indo_cg <- cg

load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net.RData")
gua_catt <- catt
# gua_cg <- cg

# use the tatt (text network attribute form) from the network we built before
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_net.RData")
```

Third, create network object using the matrices and their corresponding attributes. 

```{r}
# Indonesia coefficient network
indo_cn <- network(indo_cm, vertex.attr = indo_catt, vertex.attrnames = colnames(indo_catt),
                   directedm= F, hyper = F, loops = F, multiple = F, bipartite = F)
# Guatemala coefficient network
gua_cn <- network(gua_cm, vertex.attr = gua_catt, vertex.attrnames = colnames(gua_catt),
                   directedm= F, hyper = F, loops = F, multiple = F, bipartite = F)

# Text network
tn <- network(tm, vertex.attr = tatt, vertex.attrnames = colnames(tatt),
              directedm= F, hyper = F, loops = F, multiple = F, bipartite = F)
```


# Indonesia
## Predict ties based on same Goal

```{r}
indo <- ergm(indo_cn ~ edges + nodematch("Goal"))
summary(indo)
```
The model includes how many edges are in the graph that do not match and then how many of the edges are same-Goal (nodematch).

The coefficient on "nodematch.sex" is -0.10330, not statistically significant (p = 0.239). This means that on this network, ties based on same Goal are **less likely** than ties based on not-same Goal. We can not tell whether the indicators are correlated with an coefficient >= 0.5 based on whether they belong to the same Goal. However, because p > 0.05, we can not reject the null hypothesis that there's no relationship between "homo-goal" and ties.


## Predict ties based on same Target

```{r}
indo2 <- ergm(indo_cn ~ edges + nodematch("Target"))
summary(indo2)
```

The model includes how many edges are in the graph that do not match and then how many of the edges are same-Target (nodematch).

The coefficient on "nodematch.sex" is 0.1064, not statistically significant (p = 0.64). This means that on this network, ties based on same Target are **more likely** than ties based on not-same Target. We can not tell whether the indicators are correlated with an coefficient >= 0.5 based on whether they belong to the same Target. However, because p > 0.05, we can not reject the null hypothesis that there's no relationship between "homo-target" and ties.


# Guatemala
## Predict ties based on same Goal

```{r}
gua <- ergm(gua_cn ~ edges + nodematch("Goal"))
summary(gua)
```
coefficient = -0.33991***, p = 0.000696 
**less likely**, statistically significant


## Predict ties based on same Target

```{r}
gua2 <- ergm(gua_cn ~ edges + nodematch("Target"))
summary(gua2)
```
coefficient = -0.39575***, p = 0.0879 .  
**less likely**, statistically significant (0.1 confidence level)





# Text


## Predict ties based on same Goal

```{r}
text <- ergm(tn ~ edges + nodematch("Goal"))
summary(text)
```
coefficient = -1.63341***, p < 1e-04              
**more likely**, statistically significant 



## Predict ties based on same Target

```{r}
text2 <- ergm(tn ~ edges + nodematch("Target"))
summary(text2)
```


coefficient = 2.38935***, p < 1e-04              
**more likely**, statistically significant 


