---
title: "centrality_regression"
author: "Qinyue Hao"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

```{r}
# use the catt (coefficient network attribute form) from the network we built before
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net_sig.RData")
indo_catt <- catt

load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net_sig.RData")
gua_catt <- catt

# use the tatt (text network attribute form) from the network we built before
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_net.RData")

```






```{r}
summary(lm(degree ~ as.factor(Goal), indo_catt))
```

All else being equal, Indicators under Goal 3 has an average degree centrality score 10.75 higher than that of Goal 1. Statistically significant (p = 0.0209 < 0.05).        

All else being equal, Indicators under Goal 6 has an average degree centrality score 10.13 higher than that of Goal 1. Statistically significant (p = 0.0825 < 0.1).         

All else being equal, Indicators under Goal 7 has an average degree centrality score 11 higher than that of Goal 1. Statistically significant (p = 0.0468 < 0.05).          

All else being equal, Indicators under Goal 9 has an average degree centrality score 10.83 higher than that of Goal 1. Statistically significant (p = 0.0848 < 0.05).             

```{r}
summary(lm(degree ~ as.factor(Target), indo_catt))
```



