---
title: "QAP regression"
author: "Qinyue Hao"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE) # , cache = TRUE
```

```{r}
library(network)
library(sna)
library(dplyr)
```


**We need to admit: caveats of statistical inference with networks:**                     
In networks: Non-independence of observations            
The inference problem: The non-independence of observations affects the standard errors, not the coefficients.           
To relieve this problem, we adjust standard errors by permuting rows and columns in the matrix, while maintaining the underlying relationship. -- QAP               

**QAP – the Quadratic Assignment Procedure**         
https://www.stata.com/meeting/1nasug/simpson.pdf


# Part 1: real number matrices

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net_weighted_sig.RData")
indo_cm <- cm

# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net_weighted_sig.RData")
gua_cm <- cm

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```


## 1. QAP between text similarity and correlation coefficients -- Netork OLS Model

### Use the original value of similarity scores in text network and correlation coefficients in Indictor networks, to see:  How much the similarity between Indicator descriptions predict the positive correlation coefficient between their measurements?     

## Preprecessing:

1. To do QAP analysis (network regressions), it requires us to make the matrices in the same shape and row&column order, so I did regressions on the **common indicators** in the different matrices, and deleted the rest ones.   

2. Text similarity should only be able to help predict the positive relationships between indicators, so we kept only the positive coefficients and set the negative coefficients all to 0, so that they won't indicate any relationship that text similarity could not predict.

```{r}
indo_cmP <- indo_cm
indo_cmP[indo_cmP < 0] <- 0

gua_cmP <- gua_cm
gua_cmP[gua_cmP < 0] <- 0
```


### 1) Indonesia

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cmP), rownames(indo_cmP)]

# install.packages("sna")
library(sna)
# indo_nl_tc <- netlm(indo_tm, indo_cm)
# summary(indo_nl_tc)
indo_nl_ct <- netlm(indo_cmP, indo_tm)
summary(indo_nl_ct)
```

> Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are correlated at sqrt(0.0008313, which is the R-squared)=0.02883227, with p < 0.05, statistically significant.  

( If we did not remove the negative coefficients :
Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are correlated at sqrt(0.0005529, which is the R-squared)=0.02351383, with p < 0.05, statistically significant. ) 

 

### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cmP), rownames(gua_cmP)]

# install.packages("sna")
library(sna)
# gua_nl_tc <- netlm(gua_tm, gua_cm)
# summary(gua_nl_tc)
gua_nl_ct <- netlm(gua_cmP, gua_tm)
summary(gua_nl_ct)
```

> Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are correlated at sqrt(0.00159, which is the R-squared)=0.0398748, with p < 0.05, statistically significant.  


( If we did not remove the negative coefficients :
Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are correlated at sqrt(0.002654, which is the R-squared)=0.05151699, with p < 0.05, statistically significant. ) 


## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients -- Netork OLS Model

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Indonesia predict that of Guatemala?

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)
# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)
```

> Predicting the Indonesia coefficient network (correlation coefficients between indicators) from the Indicator text network (indicator description similarity) shows that they are correlated at sqrt(0.0001397, which is the R-squared)=0.01181948, with p > 0.05, not statistically significant.    
	

# Part 2: binary matrices

Network regression models are built to predict one binary matrix with another.     


## Preprecessing:

1. To do QAP analysis (network regressions), it requires us to make the matrices in the same shape and row&column order, so I did regressions on the **common indicators** in the different matrices, and deleted the rest ones.         

2. Make binary:             
Coefficients with an absolute value > 0 are coded as 1.            
Similarity score < 0.2 are coded as 0;         
Similarity score >= 0.2 are coded as 1;            


## load matrices data

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_coefficient_net_weighted_sig.RData")
indo_cm <- cm

# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_coefficient_net_weighted_sig.RData")
gua_cm <- cm

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```

## recode as binary

```{r}

indo_cmP <- indo_cm
indo_cmP[indo_cmP < 0] <- 0

gua_cmP <- gua_cm
gua_cmP[gua_cmP < 0] <- 0


# indo_cm[indo_cm > -0.5 & indo_cm < 0.5] <- 0
# indo_cm[indo_cm <= -0.5 | indo_cm >= 0.5] <- 1
# 
# gua_cm[gua_cm > -0.5 & gua_cm < 0.5] <- 0
# gua_cm[gua_cm <= -0.5 | gua_cm >= 0.5] <- 1

# 
# indo_cmP[indo_cmP < 0.5] <- 0
# indo_cmP[indo_cm >= 0.5] <- 1
# 
# gua_cmP[gua_cmP < 0.5] <- 0
# gua_cmP[gua_cm >= 0.5] <- 1


indo_cm[indo_cm != 0] <- 1
gua_cm[gua_cm != 0] <- 1

indo_cmP[indo_cmP != 0] <- 1
gua_cmP[gua_cmP != 0] <- 1

write.csv(colnames(indo_cmP), 
          file = "/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_positive_coeff_indicator_list.csv")
write.csv(colnames(gua_cmP), 
          file = "/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/gua_positive_coeff_indicator_list.csv")

tm[tm < 0.2] <- 0
tm[tm >= 0.2] <- 1
```

## Results and Findings (interpretation of results) 

## 1. QAP between coefficient networks and text network

### 1) Indonesia

#### a) Netork OLS Model

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cmP), rownames(indo_cmP)]

# install.packages("sna")
library(sna)
indo_nl_ct <- netlm(indo_cmP, indo_tm)
summary(indo_nl_ct)

# indo_nl_tc <- netlm(indo_tm, indo_cm)
# summary(indo_nl_tc)
```

> Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Indicator text network (whether indicator description similarity >= 0.2) with OLS network model shows that they are correlated at sqrt(3.182e-07, which is the R-squared)=0.0005640922(very little), with p > 0.05, not statistically significant. 

#### b) Logit Netork Model

```{r}
indo_nlo_ct <- netlogit(indo_cmP, indo_tm)
summary(indo_nlo_ct)
```

> Predicting the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala text network (whether indicator description similarity >= 0.2) with Network Logit Model shows that with the Guatemala text network, we can predict the Indonesia coefficient network with an 85.5% accuracy. However, p > 0.05 means we can NOT reject the null hypothesis that there's no releationship between the Indonesia Indicator coefficient network and the Indicator text network, which means there's a chance for us to see results like this just by accident.


### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cmP), rownames(gua_cmP)]

# install.packages("sna")
library(sna)
```

#### a) Netork OLS Model

```{r}
gua_nl_tc <- netlm(gua_cmP, gua_tm)
summary(gua_nl_tc)

# gua_nl_ct <- netlm(gua_cm, gua_tm)
# summary(gua_nl_ct)
```

> Predicting the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Indicator text network (whether indicator description similarity >= 0.2) with OLS network model shows that they are correlated at sqrt(0.00005693, which is the R-squared)=0.007545197(very little), with p > 0.05, not statistically significant.  ( useless )


#### b) Logit Netork Model

```{r}
gua_nlo_ct <- netlogit(gua_cmP, gua_tm)
summary(gua_nlo_ct)
```

> Predicting the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala text network (whether indicator description similarity >= 0.2) with Network Logit Model shows that with the Guatemala text network, we can predict the Indonesia coefficient network with an 67.7% accuracy. However, p > 0.05 means we can NOT reject the null hypothesis that there's no releationship between the Guatemala Indicator coefficient network and the Indicator text network, which means there's a chance for us to see results like this just by accident.
 
 
## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Guatemala predict that of Indonesia?

#### a) Netork OLS Model

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

write.csv(colnames(common_for_qap), 
          file = "/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/coefficient_network/indo_gua_common.csv")


indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)

# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)
```

> Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) with OLS Network model shows that they are correlated at sqrt(0.02229, which is the R-squared)=0.1492984, with p < 0.05 (very close to 0), statistically significant. Such small p value means that we can reject the null hypothesis that there's no releationship between the coefficient network of Indonesia and Guatemala, which means there's nearly no chance for us to see results like this just by accident.

#### b) Logit Netork Model

```{r}
nlo_2country <- netlogit(indo_cm2, gua_cm2)
summary(nlo_2country)
```

> Predicting the Indonesia coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) from the Guatemala coefficient network (whether there's a correlation coefficients >= 0.5 between indicators) with Network Logit Model shows that with the Guatemala text network, we can predict the Indonesia coefficient network with an 72.3% accuracy.             
p < 0.05 (very close to 0) means we can reject the null hypothesis that there's no releationship between the Indonesia coefficient network and the Guatemala coefficient network, which means there's very low chance for us to see results like this just by accident.
