---
title: "QAP regression"
author: "Qinyue Hao"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(network)
library(sna)
```


**We need to admit: caveats of statistical inference with networks:**
In networks: Non-independence of observations
The inference problem: The non-independence of observations affects the standard errors, not the coefficients. 
To relieve this problem, we adjust standard errors by permuting rows and columns in the matrix, while maintaining the underlying relationship. -- QAP
**QAP – the Quadratic Assignment Procedure** - https://www.stata.com/meeting/1nasug/simpson.pdf


# Part 1: real number matrices

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/indo_coefficient_matrix.RData")
indo_cm <- x
# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/gua_coefficient_matrix.RData")
gua_cm <- x

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```

## 1. QAP between text similarity and correlation coefficients

### Use the original value of similarity scores in text network and correlation coefficients in Indictor networks, to see:  How much the similarity between Indicator descriptions predict the correlation coefficient between their measurements?

### 1) Indonesia

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cm), rownames(indo_cm)]

# install.packages("sna")
library(sna)
indo_nl_tc <- netlm(indo_tm, indo_cm)
summary(indo_nl_tc)

# indo_nl_ct <- netlm(indo_cm, indo_tm)
# summary(indo_nl_ct)
```

### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cm), rownames(gua_cm)]

# install.packages("sna")
library(sna)
gua_nl_tc <- netlm(gua_tm, gua_cm)
summary(gua_nl_tc)

# gua_nl_ct <- netlm(gua_tm, gua_cm)
# summary(gua_nl_ct)
```


## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Indonesia predict that of Guatemala?

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)

## the opposite direction
# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)
```



# Part 2: binary matrices

```{r}
# 1. coefficient matrix
# Indonesia coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/indo_coefficient_matrix.RData")
indo_cm <- x
# Guatemala coefficient matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/PCA_results/gua_coefficient_matrix.RData")
gua_cm <- x

# 2. text similarity matrix
load("/Users/hailey/Documents/GitHub/G5055_Practicum_Project2/Data/Text_Model_Data/text_matrix.RData")
tm <- m
```

```{r}
indo_cm[indo_cm >= -0.5 & indo_cm < 0.5] <- 0
indo_cm[indo_cm <= -0.5 | indo_cm >= 0.5] <- 1

gua_cm[gua_cm >= -0.5 & gua_cm < 0.5] <- 0
gua_cm[gua_cm <= -0.5 | gua_cm >= 0.5] <- 1

tm[tm < 0.2] <- 0
tm[tm >= 0.2] <- 1
```


### 1) Indonesia

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
indo_tm <- tm[rownames(indo_cm), rownames(indo_cm)]

# install.packages("sna")
library(sna)
indo_nl_tc <- netlm(indo_tm, indo_cm)
summary(indo_nl_tc)

# indo_nl_ct <- netlm(indo_cm, indo_tm)
# summary(indo_nl_ct)
```




### 2) Guatemala

```{r}
# get the matrices in same shape and indicator order
# rownames(tm) # the whole list 
gua_tm <- tm[rownames(gua_cm), rownames(gua_cm)]

# install.packages("sna")
library(sna)
gua_nl_tc <- netlm(gua_tm, gua_cm)
summary(gua_nl_tc)

# gua_nl_ct <- netlm(gua_tm, gua_cm)
# summary(gua_nl_ct)
```

 
## 2. QAP between Indonesia and Guatemala Indicator correlation coefficients

### Use the original value of correlation coefficients in the Indictor networks of Indonesia and Guatemala, to see:  How much the correlation coefficient between Indicators of Indonesia predict that of Guatemala?

```{r}
diff1 <- setdiff(rownames(indo_cm), rownames(gua_cm))
common_for_qap <- setdiff(rownames(indo_cm), diff1)
# diff2 <- setdiff(rownames(gua_cm), rownames(indo_cm))
# common_for_qap <- setdiff(rownames(gua_cm), diff2) # same result 87 common indicators

indo_cm2 <- indo_cm[common_for_qap, common_for_qap]
gua_cm2 <- gua_cm[common_for_qap, common_for_qap]

nl_2country <- netlm(indo_cm2, gua_cm2)
summary(nl_2country)

# # the opposite direction
# nl_2country2 <- netlm(gua_cm2, indo_cm2)
# summary(nl_2country2)

nlo_2country <- netlogit(indo_cm2, gua_cm2)
summary(nlo_2country)


```

